NMRlipids IV: Other than PC headgroups

### 2017-03-07 Manuscript/manuscript.tex
Update manuscript

%\label{}
\section{Introduction}
Phospholipids containing various polar headgroups and acyl
chains are essential building blocks of biological membranes.
Atomistic level structural details of lipids and lipid-ion 
interactions are considered highly important in several
biological processes. The lipid structure and ion binding
can be studied in detail with NMR spectroscopy. However,
the structural interpretation of NMR data requires usage
of models. The combination of classical molecular dynamics
simulations with NMR data, especially with C-H bond
order parameters, can potentially give atomistic resolution
interpretation of structure and dynamics of molecules \cite{botan15,ollila16,ferreira16}.

Our recent studies concluded that MD models are cabable to
give structural interpretation for phosphatidylcholine 
hydrophopic acyl chain region, while hydrophilic headgrop, glycerol 
backbone and cation binding posed a major challenge for current
force fields \cite{botan15,ollila16,catte16,ferreira16}. 
These conclusions were reached by reviewing extensively 
available experimental data from various sources and using
NMRlipids Open Collaboration project to collect massive 
amount of simulation data \cite{botan15,catte16}.

Here we apply the same approach in search of MD simulation
models which would reproduce glycerol backbone and 
headgroup structures of lipids with PE, PG and PS headgroups.  
In addition, we attempt to find a MD simulation model
that would be able to correctly describe cation binding in
bilayer containing negatively charged PG and PS lipids.

>>>>

%\label{}
\section{Introduction}

In NMRlipids I and II project we were looking for a MD model
which would correctly reproduce headgroup and glycerol
backbone structures and cation binding for PC lipid bilayers \cite{botan15,catte16}.
Here we extend the same goal for other than PC lipids.
Currently the focus is on PE, PG and PS bilayers and their
mixtures with PC. Experimental data with different amounts of 
added salt is now collected and presented in this manuscript.
Simulations for bilayers containing PG and PS with low salt conditions
are ran with parameters from CHARMM GUI
and compared to experiments. Some order parameters from
simulations seems to be off from experimental values.
Simulation data from other models would be highly useful 
to see if some of the existing models would reproduce the 
experimental order parameters and to analyze different 
conformations predicted by different models respect to 
experiments.

%Phospholipids containing various polar headgroups and acyl
%chains are essential building blocks of biological membranes.
%Atomistic level structural details of lipids and lipid-ion 
%interactions are considered highly important in several
%biological processes. The lipid structure and ion binding
%can be studied in detail with NMR spectroscopy. However,
%the structural interpretation of NMR data requires usage
%of models. The combination of classical molecular dynamics
%simulations with NMR data, especially with C-H bond
%order parameters, can potentially give atomistic resolution
%interpretation of structure and dynamics of molecules \cite{botan15,ollila16,ferreira16}.

%Our recent studies concluded that MD models are cabable to
%give structural interpretation for phosphatidylcholine 
%hydrophopic acyl chain region, while hydrophilic headgrop, glycerol 
%backbone and cation binding posed a major challenge for current
%force fields \cite{botan15,ollila16,catte16,ferreira16}. 
%These conclusions were reached by reviewing extensively 
%available experimental data from various sources and using
%NMRlipids Open Collaboration project to collect massive 
%amount of simulation data \cite{botan15,catte16}.

%Here we apply the same approach in search of MD simulation
%models which would reproduce glycerol backbone and 
%headgroup structures of lipids with PE, PG and PS headgroups.  
%In addition, we attempt to find a MD simulation model
%that would be able to correctly describe cation binding in
%bilayer containing negatively charged PG and PS lipids.
